\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-01 project-writings/paper.tex
add a note for rpearl
Some notes about things

In Single Static Assignment form, each computation has a distinct
name. We take advantage of this to assign each name (that is, each
computation) a ``range''; the ranges in our system are a contiguous
subset of the set ${-\infty} \cup [-2^{31}, 2^{31}-1] \cup {\infty}$
that represent the possible results a computation may have. A range
that includes $\pm \infty$ indicates that the associated
computation may overflow in that direction.

@@

>>>>

In Single Static Assignment form, each computation has a distinct
name. We take advantage of this to assign each name (that is, each
computation) a ``range''; the ranges in our system are a contiguous
subset of the set ${-\infty} \cup [-2^{31}, 2^{31}-1] \cup {\infty}$
that represent the possible results a computation may have. A range
that includes $\pm \infty$ indicates that the associated
computation may overflow in that direction. This distinction between
the minimum/maximum 32-bit integer values and $\pm \infty$ is the key
to detecting possible overflow.

@@

At the start of range analysis, all ranges are initialized to
$[-\infty, \infty]$.

XXX: rpearl, explain how the analysis pass works; specifically, when
we add things to the worklist, because that is different from the
paper. maybe add pseudocode

Recomputation of the possible range of an instruction is fairly simple
and proceeds by the rules given in Figure \ref{fig:range_anal}. The
key insight we had in these equations is that while the ranges of the
inputs to an operation may be infinite (that is, they may have
overflowed), this possibility can be ignored when using the ranges as
inputs. This is because had the computation overflowed, it would have
been detected and IonMonkey would bail out to non-integer code. We
know that if code that assumes the input is an integer is still being
run, then the operation must not have overflowed, and thus must have a
finite range. What this means for the range analysis equations is that
we can always ``squash'' the ranges of inputs by replacing positive
and negative infinite with the maximum and minimum 32-bit integers,
respectively.
